Beta Diversity through Time and Space

### 2020-09-17 analyses/beta_diversity.Rmd
refined network analysis

### Climate data
```{r echo=FALSE, message=FALSE, include=FALSE}
gdd <- read_csv("../processed_data/climate.csv") %>%
  mutate(year = factor(year),
         yday = yday(date)) %>%
  dplyr::select(site, year, date, yday, gdd.cum) %>%
  semi_join(read_csv("../processed_data/network.csv"), by = "site")
```

@@

# Permutation tests (slow)
gdm_WN.2010.imp <- gdm.varImp(sitepair_2010.WN, geo = TRUE)
gdm_WN.2011.imp <- gdm.varImp(sitepair_2011.WN, geo = TRUE)
gdm_WN.2012.imp <- gdm.varImp(sitepair_2012.WN, geo = TRUE)

@@

format_set <- function(bio, pred) {
  formatsitepair(bio, bioFormat = 1, siteColumn = "site.day", 
                 dist = "jaccard", XColumn = "x", YColumn = "y", 
                 predData = pred, abundance = FALSE)
}

@@

# Permutations tests (slow)
gdm_survey.2010.imp <- gdm.varImp(survey_sitepair.2010, geo = TRUE)
gdm_survey.2011.imp <- gdm.varImp(survey_sitepair.2011, geo = TRUE)
gdm_survey.2012.imp <- gdm.varImp(survey_sitepair.2012, geo = TRUE)

@@

### GDM: BB observations
```{r}
# Create functions for prepping data
biodata_prep_BB <- function(net, y) {
  net %>%
    filter(year == y) %>%
    group_by(site, date, bb.sp) %>%
    summarize(count = n()) %>%
    mutate(count = rep(1, n())) %>% # this makes the data binary, which I think is what I want here; otherwise, just comment out
    spread(bb.sp, count) %>%
    replace(is.na(.), 0) %>%
    mutate(yday = yday(date)) %>%
    unite(site.day, site, yday, sep = "_", remove = "TRUE") %>%
    ungroup() %>%
    dplyr::select(-date)
}

@@

# Permutations tests (slow)
gdm_BB.2010.imp <- gdm.varImp(BB_sitepair.2010, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "./output/bb_permGDM_2010")
gdm_BB.2011.imp <- gdm.varImp(BB_sitepair.2011, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "./output/bb_permGDM_2011")
gdm_BB.2012.imp <- gdm.varImp(BB_sitepair.2012, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "./output/bb_permGDM_2012")

@@

# Plot with confidence intervals (slow)
plotUncertainty(BB_sitepair.2010, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
plotUncertainty(BB_sitepair.2011, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
plotUncertainty(BB_sitepair.2012, sampleSites = 0.7, bsIters = 10, geo  = TRUE)

>>>>

@@

# Permutation tests (slow)
gdm_WN.2010.imp <- gdm.varImp(sitepair_2010.WN, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "interaction_permGDM_2010")
gdm_WN.2011.imp <- gdm.varImp(sitepair_2011.WN, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "interaction_permGDM_2011")
gdm_WN.2012.imp <- gdm.varImp(sitepair_2012.WN, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "interaction_permGDM_2012")

@@

format_set <- function(bio, pred) {
  formatsitepair(bio, bioFormat = 1, siteColumn = "site.day", 
                 dist = "jaccard", XColumn = "x", YColumn = "y", 
                 predData = pred, abundance = FALSE) %>%
  filter(s1.elev.mean != s2.elev.mean) # this avoids comparing repeated measures of the same site (taking advantage of the fact that each site has a unique elevation in our dataset)
}

@@

# Permutations tests (slow)
gdm_survey.2010.imp <- gdm.varImp(survey_sitepair.2010, geo = TRUE, 
                              parallel = TRUE, cores = 3,
                              outFile = "survey_permGDM_2010")
gdm_survey.2011.imp <- gdm.varImp(survey_sitepair.2011, geo = TRUE, 
                              parallel = TRUE, cores = 3,
                              outFile = "survey_permGDM_2011")
gdm_survey.2012.imp <- gdm.varImp(survey_sitepair.2012, geo = TRUE, 
                              parallel = TRUE, cores = 3,
                              outFile = "survey_permGDM_2012")

@@

### GDM: BB observations; this won't work in it's present state because I cannot 
```{r}
# Create functions for prepping data
biodata_prep_BB <- function(net, y) {
  net %>%
    filter(year == y) %>%
    group_by(site, date, bb.sp) %>%
    summarize(count = n()) %>%
    mutate(count = rep(1, n())) %>% # this makes the data binary, which I think is what I want here; otherwise, just comment out
    spread(bb.sp, count) %>%
    replace(is.na(.), 0) %>%
    mutate(yday = yday(date)) %>%
    unite(site.day, site, yday, sep = "_", remove = "TRUE") %>%
    ungroup() %>%
    dplyr::select(-date)
}

@@

# Permutations tests (slow)
gdm_BB.2010.imp <- gdm.varImp(BB_sitepair.2010, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "bb_permGDM_2010")
gdm_BB.2011.imp <- gdm.varImp(BB_sitepair.2011, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "bb_permGDM_2011")
gdm_BB.2012.imp <- gdm.varImp(BB_sitepair.2012, geo = TRUE, 
                              parallel = TRUE, cores = 4,
                              outFile = "bb_permGDM_2012")

@@

# Plot with confidence intervals (slow)
p <- plotUncertainty(BB_sitepair.2010, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
plotUncertainty(BB_sitepair.2011, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
plotUncertainty(BB_sitepair.2012, sampleSites = 0.7, bsIters = 10, geo  = TRUE)
